Tor's Usability for Censorship Circumvention

### 2016-04-04 pets2017-paper/pets2017-paper.tex
Fix \bibliography call (wrong filename).

An empirical evaluation of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in section {\color{red} TODO}. A heuristic evaluation of the existing interface
and new interface can be found  in section {\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in section {\color{red} TODO}.

@@

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
After their interview, participants were informed that the experiment was over and 
given their payment of \$30.

%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
%    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
%    \item {\bfseries Time to Completion} Time to complete, ease of user for the average user. 
%    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak %that they are using Tor. 
%\end{enumerate}

We noticed four common challenges:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Challenge 1:} Users don't know how to choose between connecting directly to the Tor network or manually configuring their connection (Figure \ref{fig:window1}). The text was unread or not understood by most users. When the user read the text, they found no instructions, but were given information to make a decision for themselves, which they did not feel equipped to do.  
\item {\bfseries Challenge 2:} Users feel compelled to set up a bridge, even if they don't need one. We believe this is due to the text on the first screen, which refers to a ``censored internee connection'' (Figure \ref{fig:window1}). Bridges are only necessary when the government actively censored Tor relays, but participants are not able to determine the difference between a censor that blocks websites and a censor that blocks websites and the Tor network. 
\item {\bfseries Challenge 3:} Users did not know what to do after a failure. Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
\item {\bfseries Challenge 4:} Users draw incorrect conclusions after a failed connection. The interface passively re-displayed the last window seen before the attempted connection (Figure \ref{fig:window4} or \ref{fig:window5}), regardless of the error.
\end{itemize}

%configure vs connect
\begin{quotation}
\noindent{\bfseries P10}: \textit{``I was censored, so I picked the configure.''}\\
\noindent{\bfseries P9}: \textit{``Configure seemed manual, so I clicked connect.''}\\
\noindent{\bfseries P14}:\textit{``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect..''} 
\end{quotation}

%time
\begin{quotation}
\noindent{\bfseries P16}:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
\noindent{\bfseries P6}:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
\noindent{\bfseries P1}:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
\end{quotation}

%lack of knowledge 
\begin{quotation}
\noindent{\bfseries P16}:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}\\
\noindent{\bfseries P12}:\textit{``I decided which options to choose by process of elimination with trial and error..''}\\
\noindent{\bfseries P2}:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
 means at all."}\\
 \noindent{\bfseries P3}:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
 \noindent{\bfseries P4}:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
\end{quotation}

%misc
\begin{quotation}
\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''} 
\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
\end{quotation}

%bridges
\begin{quotation} 
\noindent{\bfseries P7}:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is. Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}\\
\noindent{\bfseries P8}:\textit{``I have no clue what's the difference between flashrpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?'}
\end{quotation}

\begin{quotation}
\noindent{\bfseries P4}:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
\noindent{\bfseries P5}:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
\end{quotation}

%proxies
\begin{quotation}
\noindent{\bfseries P11}:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
\noindent{\bfseries P15}:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
\end{quotation}

@@

\bibliographystyle{abbrv}
\bibliography{pets-2017-paper.bib}

>>>>

An exploration of the problems with the existing Tor Browser 
configuration interface through user observation and interviews can be 
found in section {\color{red} TODO}. A heuristic evaluation of the existing interfaceand new interface is in section {\color{red} TODO}. We empirically show 
that the redesigned interface improves completion rate, reduces time to completion, 
and provides a safe path for at-risk users in section {\color{red} TODO}.

@@

After users completed the browsing tasks or have spent the rest of the time
trying to configure Tor Browser, we interviewed participants about their experience.
We performed a live transcription of the interview to avoid recording voices, which is
considered personally identifying information. 
We asked three standard questions asking about their general experience, 
confusing interface features, and soliciting feedback for improvements. We followed up
with specific questions we had for a particular participant from observing their screen. 
This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
After their interview, participants were informed that the experiment was over and 
given their payment of \$30.

\subsubsection{Results} 
{\color {red} meta couple-sentence summary of the feeling we get from the experiment. All quotes are paraphrase from a live transcription.}\\

\noindent {\bfseries Connect vs. Configure} 
The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection. Text in the interface tells people that connecting directly ``will work in most situations'' and instructs to configure a bridge or proxy if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.

The participant across all censorship environments connected directly to the Tor network. When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process. 
\begin{quotation}
\noindent P9: \textit{``Configure seemed manual, so I clicked connect.''}\\

\noindent P14:\textit{``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect..''} 
\end{quotation}

Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this happens, or what the difference between a blocked website and a blocked relay looks like. Participant 10 and several other participants in the mild censorship environment opted to configure a connection when a direct connection to the Tor network would have worked.

\begin{quotation}
\noindent P10: \textit{``I was censored, so I picked the configure.''}
\end{quotation}

This mistake can results in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments. Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.

Making the choice between connect and configure clearer for users has the possibility to save time and keep users safer. Waiting for a failed connection takes about couple minutes, so users can save at least that time by making the correct decision the first time. Users who need to configure can benefit from not clicking connect, which keeps them safer by not leaving a detectable network trace that indicates that they are trying to use Tor to circumvent censorship.\\

\noindent {\bfseries Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.

\begin{quotation}
\noindent P7:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.''}\\
\noindent P12:\textit{``I decided which options to choose by process of elimination with trial and error.''}
\end{quotation}

When a participant chooses to configure a bridge, they are faced with a list of options without much explanation. 
\begin{quotation} 
\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}\\
\noindent P8:\textit{``I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?'}
\end{quotation}

\begin{quotation}
\noindent P4:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
\noindent P5:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
\end{quotation}

\noindent {\bfseries Proxy Configuration} 
If users did not successfully connect on their first attempt, they did not know what to do next. Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.). Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection. Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
%proxies
\begin{quotation}
\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
\end{quotation}

\noindent{\bfseries Sources of Frustration} 
%time
\begin{quotation}
\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
\end{quotation}

%lack of knowledge 
\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
 means at all."}\\
 \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
 \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}\\
 \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
\end{quotation}

%\begin{quotation}
%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
%\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
%\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
%\end{quotation}

@@

\bibliographystyle{abbrv}
\bibliography{pets2017-paper}
